The eclipse of ASASSN-21qj

### 2022-09-14 src/tex/ms.tex
[showyourwork] overleaf sync

   \author{M. Kenworthy
          \inst{1}
          \and
          Arttu Sainio
          \inst{2}
          \and
          Eric E. Mamajek
          \inst{3}
          \and
          Joeseph Masiero
          \inst{4}
          \and 
          Amy Mainzer
          \inst{4}
          \and
          Joeseph (Davy) Kirkpatrick
          \inst{4}
          \and 
          Grant M. Kennedy
          \and
          NEOWISE authorship list
          \inst{4}
          }

   \institute{Leiden Observatory, University of Leiden,
   PO Box 9513, 2300 RA Leiden, The Netherlands\\
   \email{kenworthy@strw.leidenuniv.nl}
         \and
             Arttu's address ...\\
    \and
    JPL
    \and
    Caltech/IPAC, 1200 E California Blvd, Mail Code 100-22, Pasadena, CA 91125, USA}

   \date{Received XXXX; accepted XXXX}

@@

   The star (Gaia EDR3 source 5539970601632026752 at RA=08:15:23.2996, DEC=-38:59:23.304, $d\sim 556$ pc, G=13.4 mag, BP-RP=0.8 mag) underwent a sudden dimming event in December 2021, which was announced by \citet{RizzoSmith21} and assigned the identifier ASASSN-21qj.
   %
   The star has subsequently maintained rapidly fluctuating photometry through to August 2022 \citep{RizzoSmith22} and has been monitored intensively by the AAVSO observers and the LCOGT network of telescopes.
   %
   It had previously shown no significant stellar variation in the optical bands for 9600 days as reported in \citet{RizzoSmith21}.
   %
   Searches through other photometric archives showed no other significant changes in the optical bands before this epoch.
   %
   The wide field infrared satellite WISE has photometric imaging from 3.8 microns (band W1) through to 25 microns (band W4), and the NEOWISE survey has photometry for bands W1 and W2 for this star.
   %
   This star showed a significant brightening of 0.7 magnitudes in W1 and 0.8 magnitudes in W2 between two observing epochs (65000 MJD and 65120 MJD), and the IR color of the star had changed from W1-W2=0.0 to 1.2, but no significant changes in flux in the optical bands were seen during this time.
   %
   Some 900 days later, the dimming was seen in the optical, and the absorption is larger at shorter optical wavelengths.
   %
   These observations are all consistent with an event that generated a significant amount of sub-micron dust which subsequently started to transit the stellar disk.

@@

@@

@@

>>>>

   \author{M. Kenworthy
          \inst{1}
          \and
          Arttu Sainio
          \inst{2}
          \and
          Eric E. Mamajek
          \inst{3}
          \and
          Joeseph Masiero
          \inst{4}
          \and 
          Amy Mainzer
          \inst{4}
          \and
          Joeseph (Davy) Kirkpatrick
          \inst{4}
          \and 
          Grant M. Kennedy
          \and
          NEOWISE authorship list
          \inst{4}
          \and
          AAVSO observers
          \and
          St\'{e}phane Charbonnel
          \and
        Olivier Garde
        \and
        Pascal Le D\^{u}
        \and
        Lionel Mulato
        \and
        Thomas Petit
          }

   \institute{Leiden Observatory, University of Leiden,
   PO Box 9513, 2300 RA Leiden, The Netherlands\\
   \email{kenworthy@strw.leidenuniv.nl}
         \and
             Arttu's address ...\\
    \and
    JPL
    \and
    Caltech/IPAC, 1200 E California Blvd, Mail Code 100-22, Pasadena, CA 91125, USA
    \and
    NEOWISE
    \and
    AAVSO people
    \and
    XXXX
}
   \date{Received XXXX; accepted XXXX}

@@

   The star (Gaia EDR3 source 5539970601632026752 at RA=08:15:23.2996, DEC=-38:59:23.304, $d\sim 556$ pc, G=13.4 mag, BP-RP=0.8 mag) underwent a sudden dimming event in December 2021, which was announced by \citet{RizzoSmith21} and assigned the identifier ASASSN-21qj.
   %
   The star has subsequently maintained rapidly fluctuating photometry through to August 2022 \citep{RizzoSmith22} and has been monitored intensively by the AAVSO observers and the LCOGT network of telescopes.
   %
   It had previously shown no significant stellar variation in the optical bands for 2300 days as reported in \citet{RizzoSmith21}.
   %
   Searches through other photometric archives showed no other significant changes in the optical bands before this epoch.
   %
   The wide field infrared satellite WISE has photometric imaging from 3.8 microns (band W1) through to 25 microns (band W4), and the NEOWISE survey has photometry for bands W1 and W2 for this star.
   %
   This star showed a significant brightening of 0.7 magnitudes in W1 and 0.8 magnitudes in W2 between two observing epochs (65000 MJD and 65120 MJD), and the IR color of the star had changed from W1-W2=0.0 to 1.2, but no significant changes in flux in the optical bands were seen during this time.
   %
   Some 900 days later, the dimming was seen in the optical, and the absorption is larger at shorter optical wavelengths.
   %
   These observations are all consistent with an event that generated a significant amount of sub-micron dust which subsequently started to transit the stellar disk.

@@

\begin{figure}
   \begin{centering}
   \includegraphics[width=\hsize]{figures/mie_single.pdf}
      \caption{Mie test.}
      \label{fig:mietest}
      \script{plot_mie_single.py}
      \end{centering}
\end{figure}

@@

\subsection{ROAD Photometry}

@@

\subsection{2SPOT spectroscopy}

For the observations and setup : 
Ritchey-Chretien telescope of 12 inch in diameter (305mm) open at $f/5$ (with focal reducer CCD 67 astrophysics).
%
Equatorial mount GM 3000 HPS from 10 micron (https://www.10micron.com/en/product/gm3000-hps/)

The spectrograph is a Spectrograph Alpy 600 $R=570$ with a $23\mu m$ wide slit (https://www.shelyak.com/produit/alpy-600/?lang=en) and an ATIK 414ex camera. (https://www.atik-cameras.com/product/atik-414ex/)

The observation site is in Chile at Deep Sky Chile (https://www.deepskychile.com/en/)

Lon : 70°W 51’ 11,86’'
Lat : 30°S 31’ 34,71 »
Alt : 1700m AMSL

For this spectrum : 3 exposures of 1200s each in bin 1x1 taken in automatic mode with Prism V11 Software (https://www.prism-astro.com/) , spectrum process with ISIS software (http://www.astrosurf.com/buil/isis-software.html)
Date : 07/09/2022 at 8h34’52’ UTC (middle time exposure) JJ Date : 2459829,8785

And for more informations about 2SPOT, you wil find many informations in our website : https://2spot.org/EN/
and also information about the team : https://2spot.org/EN/equipe.php

\begin{figure*}
   \begin{centering}
   \includegraphics[width=\textwidth]{figures/2spot_spectrum.pdf}
      \caption{2plot spectrum showing features of a G type star.
      %
              }
              \label{fig:2spotspectrum}
              \script{plot_2spot_spectrum.py}
              \end{centering}
       \end{figure*}
